\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-11-09 k-planar.tex
Notes
Went back to old definition of crossing and removed incorrect statement about two edges crossing at most once.

We first formally define $k$-planar graphs.  For a surface $\Sigma$,  a \defin{$\Sigma$-embedded graph} $G$ is a graph with $V(G)\subset\Sigma$ in which each edge $vw\in E(G)$ is a curve\footnote{A \defin{curve} in a surface $\Sigma$ is a continuous function $f:[0,1]\to \Sigma$. The points $f(0)$ and $f(1)$ are called the \defin{endpoints} of the curve.  When there is no danger of misunderstanding we treat a curve $f$ as the point set $\{f(t):0\le t\le 1\}$.  The \defin{interior} of $f$ is the point set $\{f(t):0<t<1\}$.} in $\Sigma$ with endpoints $v$ and $w$ and not containing any vertex of $G$ in its interior. The \defin{faces} of $G$ are the connected components of $\R^2\setminus \bigcup_{vw\in E(G)} vw$. A \defin{crossing} in a $\Sigma$-embedded (multi)graph $G$ is an unordered pair of distinct edges $\{vw,xy\}\subseteq E(G)$ whose interiors have a point in common.

If an embedded graph $G$  has no crossings then it is \defin{non-crossing} graph.  When $G$ is non-crossing and $F$ is a face of $G$, then let \defin{$V(F)$} be the set of vertices in $G$ on the boundary of $F$.  When $F$ is homeomorphic to a disk, the \defin{facial walk} of $F$ is the cycle consisting of the edges and vertices of $G$ on the boundary of $F$.  If  $\Sigma=\R^2$ is the Euclidean plane and each edge of $G$ is involved in at most $k$ crossings, then $G$ is a $k$-plane graph.  A graph $G$ is \defin{$k$-planar} if is isomorphic to some $k$-plane graph.  A $0$-plane graph is a \defin{plane} graph and a $0$-planar graph is a \defin{planar} graph.

Without any loss of generality we may assume that the interiors of any two edges of a $\Sigma$-embedded graph $G$ have at most one point in common and that no point in $\R^2$ is contained in the interior of three or more edges of $G$.  This assumption can be enforced by local changes that do not change the number of crossings each edge is involved in.  If $p$ is a common point in the interior of two crossing edges $vw$ and $xy$, then we say that $vw$ and $xy$ \defin{cross at} $p$.

@@

\note{DW}{The word ``interior'' may be misinterpreted when refering to the outerface (see referee's comment). Shall we just write ``contained in some face''? Do we need to change this elsewhere?}
\note{PM}{Done.  Changing occurrences elsewhere also.}

>>>>

We first formally define $k$-planar graphs.  For a surface $\Sigma$,  a \defin{$\Sigma$-embedded graph} $G$ is a graph with $V(G)\subset\Sigma$ in which each edge $vw\in E(G)$ is a curve\footnote{A \defin{curve} in a surface $\Sigma$ is a continuous function $f:[0,1]\to \Sigma$. The points $f(0)$ and $f(1)$ are called the \defin{endpoints} of the curve.  When there is no danger of misunderstanding we treat a curve $f$ as the point set $\{f(t):0\le t\le 1\}$.  The \defin{interior} of $f$ is the point set $\{f(t):0<t<1\}$.} in $\Sigma$ with endpoints $v$ and $w$ and not containing any vertex of $G$ in its interior. The \defin{faces} of $G$ are the connected components of $\Sigma\setminus \bigcup_{vw\in E(G)} vw$.
If some point $p\in\Sigma$ is a common point in the interior of two distinct edges $vw$ and $xy$, then we say that $vw$ and $xy$ \defin{cross at} $p$ and we call the pair $(\{vw,xy\},p)$ a \defin{crossing} in $G$.  Without any loss of generality we may assume that no point in $\Sigma$ is contained in the interior of three or more edges of $G$.  This assumption can be enforced by local changes that do not change the number of crossings each edge is involved in.

% A \defin{crossing} in a $\Sigma$-embedded (multi)graph $G$ is a pair $(\{vw,xy\},p)$ where $vw$ and $xy$ are distinct edges of $G$ and $p$ is a point that is in the interior of both $vw$ and $xy$.

If an embedded graph $G$  has no crossings then it is \defin{non-crossing}.  When $G$ is non-crossing and $F$ is a face of $G$, then let \defin{$V(F)$} be the set of vertices in $G$ on the boundary of $F$.  When $F$ has a single boundary component, the \defin{facial walk} of $F$ is the walk consisting of the edges and vertices of $G$ on the boundary of $F$ in the cyclic order they are encountered while traversing the boundary of $F$.  If  $\Sigma=\R^2$ is the Euclidean plane and each edge of $G$ is involved in at most $k$ crossings, then $G$ is a $k$-plane graph.  A graph $G$ is \defin{$k$-planar} if it is isomorphic to some $k$-plane graph.  A $0$-plane graph is a \defin{plane} graph and a $0$-planar graph is a \defin{planar} graph.

@@

\note{DW}{The word ``interior'' may be misinterpreted when refering to the outerface (see referee's comment). Shall we just write ``contained in some face''? Do we need to change this elsewhere?}
\note{PM}{Done.  I've changed occurrences elsewhere also.  Under our definitions (in Section 2.3) the faces of $G$ are open sets so in $F$ already means in the interior of $F$.  In one instance, I changed ``"``in the interior or boundary of $F$'' to ``in the closure of $F$.''}
